Appendix S1: Supporting Information

### 2021-09-02 ms/SI.Rmd
Change latitudinal area var to "lat_area"
from just "area", so as not to confuse with "area" of protected zones

a <- plot_env("a", "Area", "area", "km^2")
b <- plot_env("b", "% apomictic taxa", "percent_apo", labels = function(x) scales::percent(x, accuracy = 1))
c <- plot_env("c", "Precipitation", "precip", "mm")
d <- plot_env("d", "Precip. season.", "precip_season" , "")
e <- plot_env("e", "Temperature", "temp", "°C", function(x) x/10)
f <- plot_env("f", "Temp. season.", "temp_season")

>>>>

a <- plot_env("a", "Area", "lat_area", "km^2")
b <- plot_env("b", "% apomictic taxa", "percent_apo", labels = function(x) scales::percent(x, accuracy = 1))
c <- plot_env("c", "Precipitation", "precip", "mm")
d <- plot_env("d", "Precip. season.", "precip_season" , "")
e <- plot_env("e", "Temperature", "temp", "°C", function(x) x/10)
f <- plot_env("f", "Temp. season.", "temp_season")
